QPLIB: A Library of Quadratic Programming Instances

### 2017-01-27 methods.tex
show list of todos up front, minor changes
Add files via upload

The solvers in Table \ref{t:solvers} which implement incomplete methods for continuous NLPs (a problem class containing QCQ) are \conopt, \ipopt, \minos, \snopt, and \knitro. The methods are local search algorithms and are essentially of the following types: %Note that traditionally \knitro used to be a local (nonconvex) NLP solver.
%All of these solvers implement essentially three types of local search methods for continuous NLPs:
\todo{sequential linear programming, sequential quadratic programming, trust-region}
\begin{itemize}
 \item active set methods (\conopt, \minos, \snopt, \knitro) \cite{Dost09};
 %
 \item interior point methods (\ipopt, \knitro) \cite{Wright97};
 %
 \item projected gradient methods \cite{CalaMore87:mp,ChenGui13:coap}.
\end{itemize}
%
Active set and interior point methods have been defined for *C* but also for general (continuous) NLPs. In fact, all of the solvers named above target this larger problem class.

@@

The solvers in Table \ref{t:solvers} which implement asymptotically complete methods are \oqnlp, \msnlp, \knitro, and certain sub-solvers of \lgo. Specifically, we consider the following methods:
%
\begin{itemize}
 \item global adaptive random search (\lgo GARS);
 %
 \item multi-start (\knitro, \lgo MS, \msnlp, \oqnlp); specifically, the former three apply to QCQ whereas the latter to QGQ.
\end{itemize}

@@

In general, the applicability of meta-heuristics to a given problem depends 
on whether the local search they utilize
%on what whether the local search they rest on 
addresses that problem or not. 
\todo[inline]{Antonio: the concept of ``addresses that problem'' is not very clear to me, this sentence may benefit from rephrasing (or the paragraph from deleting if it's not deemed to be utterly necessary).} Depending on the local search employed, Multi-start methods can address MINLP of the most general class.

>>>>

The solvers in Table \ref{t:solvers} which implement incomplete methods for continuous NLPs (a problem class containing QCQ) are \conopt, \ipopt, \minos, \snopt, and \knitro. Note that all these solvers tackle the more general class of continuous NLP, while we use them only for the considerably more restricted class of QP. While there are many different approaches for continuous NLPs in general, we therefore describe here on those that are particularly well-suited for QP, i.e.:
%
\begin{itemize}
 \item active set methods (\conopt, \minos, \snopt, \knitro) \cite{Dost09};
 %
 \item interior point methods (\ipopt, \knitro) \cite{Wright97};
 %
 \item projected gradient methods \cite{CalaMore87:mp,ChenGui13:coap}.
\end{itemize}
%
Active set and interior point methods have been defined for *C* but also for general (continuous) NLPs. In fact, all of the solvers named above target this larger problem class.

@@

The solvers in Table \ref{t:solvers} which implement asymptotically complete methods are \oqnlp, \msnlp, \knitro, and certain sub-solvers of \lgo. Specifically, we consider the following methods:
%
\begin{itemize}
 \item global adaptive random search (\lgo);
 %
 \item multi-start (\knitro, \lgo, \msnlp, \oqnlp); specifically, the former three apply to QCQ whereas the latter to QGQ.
\end{itemize}

@@

In general, the applicability of meta-heuristics to a given problem relies on availability of a local search that exploit the structural properties of the problem. 
Depending on the local search employed, Multi-start methods can address MINLP of the most general class.
